\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
  \textbf{\Huge May Tsai} \\
  \vspace{8pt}
  \small
  \faMobile \hspace{.5pt} \href{tel:+886971820295}{(+886) 971-820-295}
  $\cdot$
  \faAt \hspace{.5pt} \href{mailto:maytsai504@gmail.com}{maytsai504@gmail.com}
  $\cdot$
  \faGlobe \hspace{.5pt} \href{https://maytsai.com}{maytsai.com}
\end{center}

%----------- EDUCATION -----------

\section{Education}
\resumeSubHeadingListStart
  \resumeEducationHeading
    {National Taiwan University (NTU)}{Taipei, Taiwan}
    {B.A. in Agricultural Economics, 2nd Year}{Sep 2024 \textbf{--} Jun 2028}
  \resumeItemListStart
    \resumeItem{\textbf{Relevant coursework:} Principles of Economics, Microeconomics, Statistics, Applied Econometrics, Trade Liberalization and Taiwan Agriculture}
  \resumeItemListEnd

  \vspace{3pt}

  \resumeEducationHeading
    {The Affiliated Senior High School of National Taiwan Normal University}{Taipei, Taiwan}
    {High School Diploma}{Sep 2021 \textbf{--} Jun 2024}
  \resumeItemListStart
    \resumeItem{One of the most selective high schools in Taiwan, admitting the top 2\% of students nationally.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
\resumeSubHeadingListStart

  \resumeSubheading
    {Taiwan--Japan Agricultural Trade Academic Exchange}{Taipei, Taiwan}
    {National Taiwan University}{Nov 2025}
    \resumeItemListStart
      \resumeItem{Conducted independent research on Taiwan's agricultural trade dynamics and compiled findings into a bilingual English poster for an international academic exchange with Yokohama National University.}
      \resumeItem{Defended policy arguments under live questioning from Japanese counterparts, navigating differing economic frameworks and perspectives across language barriers.}
      \resumeItem{Initiated substantive dialogue on tariff structures and food security that extended beyond the formal session, earning commendation from faculty advisors on both sides.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------

\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {International Student Receptionist}{Taipei, Taiwan}
    {National Taiwan University}{Sep 2025 \textbf{--} Present}
    \resumeItemListStart
      \resumeItem{Onboarded incoming exchange students from Japan, Thailand, and France, providing personalized guidance on academic systems, housing, and daily life in Taiwan.}
      \resumeItem{Built sustained cross-cultural relationships that extended beyond orientation, acting as an ongoing resource and point of connection for international students on campus.}
    \resumeItemListEnd

  \resumeSubheading
    {Secretary}{Taipei, Taiwan}
    {NTU Surf Club}{Sep 2025 \textbf{--} Present}
    \resumeItemListStart
      \resumeItem{Lead club administration including venue procurement, government grant applications, and end-to-end logistics for multi-day surfing camps attended by 50+ members.}
      \resumeItem{Served as the primary point of contact for crisis resolution during events, maintaining operational continuity and morale under pressure.}
    \resumeItemListEnd

  \resumeSubheading
    {Private Tutor for International Students}{Taipei, Taiwan}
    {Self-employed}{Aug 2025 \textbf{--} Present}
    \resumeItemListStart
      \resumeItem{Delivered comprehensive English instruction across core academic subjects to an international elementary student, tailoring lesson plans to individual learning pace and needs.}
      \resumeItem{Designed structured Mandarin curriculum for international students from scratch, achieving measurable progress in reading and conversational fluency within weeks.}
    \resumeItemListEnd

  \resumeSubheading
    {Camp Lead}{Hualien, Taiwan}
    {Rural Service Learning Program}{Feb 2025 \textbf{--} Aug 2025}
    \resumeItemListStart
      \resumeItem{Designed and led an economics education camp for elementary students in an underserved rural community in Hualien, covering curriculum development and on-site facilitation.}
      \resumeItem{Translated university-level economic concepts into age-appropriate, hands-on activities, making abstract ideas accessible and engaging for young learners with no prior exposure.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- LANGUAGE PROFICIENCY -----------

\section{Language Proficiency}
\resumeSubHeadingListStart
  \small{\item{
    \textbf{English:} IELTS 7.5 (CEFR C1) \hspace{10pt}
    \textbf{Spanish:} Completed University-level Spanish I (A1) \hspace{10pt}
    \textbf{German:} A1 in progress
  }}
\resumeSubHeadingListEnd

%----------- INTERESTS -----------

\section{Interests}
\resumeSubHeadingListStart
  \small{\item{Swimming, piano, guitar, surfing, photography, and handcrafts}}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
